The Astropy Project

### 2017-12-08 main.tex
Final edit to my edits

Astronomers dealing with observational imaging commonly need to make figures
with images that include the correct coordinates and optionally display a
coordinate grid. The challenge, however, is that the conceptual coordinate axes
(such as longitude/latitude) need not be lined up with the pixel axes of the
image. The \package{astropy.visualization.wcsaxes} subpackage implements a
generalized way of making figures from an image array and a world coordinate
system (WCS) object that provides the transformation between pixel and
world coordinates.

@@

Beyond the core code, the \astropy project is also further developing the
\astropy-managed affiliated packages.
While these may not be integrated into the \astropypkg core package, these
projects provide code that are useful to the astronomical community and meet the
testing and documentation standards of \astropy.
Some of these new efforts include an initiative to develop tools for
spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and support for HEALPIX
projection. %\citep{astropy-healpix}
%\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}

>>>>

Astronomers dealing with observational imaging commonly need to make figures
with images that include the correct coordinates and optionally display a
coordinate grid. The challenge, however, is that the conceptual coordinate axes
(such as longitude/latitude) need not be lined up with the pixel axes of the
image. The \package{astropy.visualization.wcsaxes} subpackage implements a
generalized way of making figures from an image array and a WCS object
that provides the transformation between pixel and world coordinates.

@@

Beyond the core code, the \astropy project is also further developing the
\astropy-managed affiliated packages.
While these may not be integrated into the \astropypkg core package, these
projects provide code that is useful to the astronomical community and meet the
testing and documentation standards of \astropy.
Some of these new efforts include an initiative to develop tools for
spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and support for HEALPIX
projection. %\citep{astropy-healpix}
%\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
